### 2020-08-08 Analysis/Code/Paper.Rmd
Added the ability to render as HTML

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex

>>>>

 author: "Dmitry Sorokin"
 date: "`r format(Sys.time(), '%B %d, %Y')`"
 classoption: pagebackref # passes pagebackref=true to hyperref before it is loaded, allowing backreferencing
 output:
  pdf_document:
    keep_tex: true
    fig_height: 2.5
    fig_width: 6
    number_sections: true
    citation_package: natbib
    extra_dependencies:
       footmisc: ["bottom"] # footnote management
       setspace: ["doublespacing"] # spacing of the paper
       caption: ["tableposition=top"]
       dsfont: null # indicator function 1
       booktabs: null
       makecell: null
    includes:
       in_header: extra_header.tex
  html_document:
    fig_height: 2.5
    fig_width: 6
    number_sections: true
